%-------------------------
% Resume in Latex
% Author : Kenil Patel
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://pkenil96.github.io/}{\Large Kenil Patel}} & Email : \href{mailto:kenspatel96@gmail.com}{kenspatel96@gmail.com}\\
  \href{https://pkenil96.github.io}{https://pkenil96.github.io} & Mobile : 9994739300 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Vellore, TN}
      {Bachelor of Technology in Computer Science;  GPA: 3.71 (9.28)}
      {Jul. 2014 -- Aug. 2018}
  \resumeSubHeadingListEnd
%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Netskope}{Bangalore, KA}
      {Member of Technical Staff}{Jul 2018 - Present}
      \resumeItemListStart
        \resumeItem{Signature Development}
          {Core company product that extracts unique patterns from HTTP(s) traffic to identify activities like Upload, Download, Share, Post etc and let the customer impose fine-grained policies.}
        \resumeItem{Reverse Proxy}
          {Worked with Reverse proxy deployment team. Developed rewrite rules and callbacks to bring customer traffic to Netskope Proxy(Python, JSON, YAML, SAML, SSO).}
        \resumeItem{Stack Management}
          {Responsible for upgrading, debugging local stacks and provisioning new VM(s) on AWS, KVM and ESXi (Jenkins, Ansible).}
        \resumeItem{Research and Patent}
          {Worked with the co-founder to develop and patent rights for  Storage Constraint Profile feature for Netskope IaaS team; Metadata-Based Data Loss Prevention(DLP) for Cloud Resources.}
        \resumeItem{Log Parser}
          {Developed python tool to extract valuable data from production logs, used for monitoring critical alerts and taking proactive steps. (Python)}
      \resumeItemListEnd

    \resumeSubheading
      {Netskope}{Bangalore, KA}
      {Software Developer Intern}{Jan 2014 - Jul 2014}
      \resumeItemListStart
        \resumeItem{Content developer}
          {Cloud apps traffic analysis and signature writing for AWS CLI and SDK(s) (Fiddler, Wireshark, TCPdump)}
        \resumeItem{UT coverage}
          {Wrote unit tests for reverse proxy backend as part of company's CICD integration. (Pytest, Unittest, Flask)}
        \resumeItem{Inline team automation}
          {Developed a python tool to automate feature testing and improve quality for signatures.}
      \resumeItemListEnd

    \resumeSubheading
      {Bhaskaracharya Institute For Space Applications and Geo-Informatics}{Gandhinagar, GJ}
      {Research Summer Intern}{May 2017 - Jul 2017}
      \resumeItemListStart
        \resumeItem{Dynamic map composition in GIS}
          {Developed dynamic map printing tool to study the pattern of voters in Gujarat's rural area. Worked on Openlayers, Mapfish, JS and Geoserver.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{SecureBox}
      {Backup and update utility created as part of System Design course. Backing up important files from managed devices to the cloud and fetching updates from cloud to the local system.}
    \resumeSubItem{AutoCompleteMe}
      {Did this project under Data Structures course at VIT. Created a simple Dictionary using Java Swing ADT and Trie data structure and tested this application using half a million strings.}
    \resumeSubItem{GreVocabInContext}
      {Scrape well-known news sites like The Hindu/Hindustan Times and extract the paragraph that has the input GRE word.}
    \resumeSubItem{LogParser}
      {Developed a python tool to extract valuable data from thousands of lines of production logs.}
    \resumeSubItem{UniversityCourseBuilder}
      {Developed a C++ program using topological sort that checks the prerequisite courses and lists best possible combination for students.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, C++, Javascript, SQL}
      \hfill
      \textbf{Technologies}{: AWS, Kafka, SAML, Ansible, Jenkins, Mongo}
    }
  \resumeSubHeadingListEnd


%--------Honours and Awards-------------
\section{Honours and Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{Chief Minister Schlarships}
      {Recepient of CMS scholarships awarded to the top 10 percent high school students across the country. (Hon. chief minister scholarship scheme, Gujarat Govt, 2014}
    \resumeSubItem{Cent percent attendance award}
      {Recepient of 100 percent attendance award for maintaining full attendance during undergraduate feshman year. (VIT University, 2015)}
  \resumeSubHeadingListEnd

\end{document}